---
title: "HW3"
author: "Stephen Powers"
date: "9/26/2019"
output: github_document
---


```{r setup, include = FALSE}
  knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r }
library(readxl)
library(tidyverse)
```

### Importing and Cleaning Data

### *TrashWheel Data*

```{r}
TrashWheel = 
  read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",
                        sheet = 1) %>%
  janitor::clean_names() %>%
  drop_na (dumpster) %>%
  mutate(sports_balls = as.integer(sports_balls))
```

### *2017 Precipitation Data* 


```{r}
Precipitation_2017 =
  read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",
                        sheet = "2017 Precipitation", skip = 1) %>%
  janitor::clean_names() %>%
  drop_na(total) %>%
  mutate(year = "2017")
```

### *2018 Precipitation Data* 


```{r}
Precipitation_2018 = 
  read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",
                        sheet = "2018 Precipitation", skip = 1) %>%
  janitor::clean_names() %>%
  drop_na(total) %>%
  mutate(year = "2018")
```

### *Combining Precipitation Data* 

```{r}
Precipitation_2017_2018 = 
  bind_rows(Precipitation_2017, Precipitation_2018) %>%
  mutate(month = month.name[month]) %>%
  select(year, month, total)
```

There are `r nrow(TrashWheel)` observations in the Mr. Trash Wheel dataset. There here are `r nrow(Precipitation_2017_2018)` observations in the combined precipitation dataset. Key variables in the Mr. Trash Wheel data set includes total weight (weight_tons), volume (volume_cubic_yards), and number of specific items (e.g. plastic_bottles, glass_bottles, chip_bags) collected by individual dumpsters, and the date collected is also included. 


## Problem 2

```{r}

```

## Problem 3

```{r}

```

